\documentclass[main.tex]{subfiles}



\setlength{\columnsep}{30pt}

\begin{document}
\pagestyle{style3}
\newgeometry{left=0.8in,right=2.8in, top=3.5cm,bottom=2cm}

\begin{fullwidth}
\begin{multicols*}{2}
\noindent\begin{bf}Online classes might not be for you?\end{bf}\parThink about the reasons why you signed up to this online class. On one hand, you might have signed to this class because you are truly interested in online education and because you feel you can succeed. If this is the case, I congratulate you! I am certain this hybrid class will suit your needs. On the other hand, you might have signed up because there were no more sits in any face-to-face class at the most convenient times for you. If this is the case, I have to warn you: chances are this class is not for you. And more importantly, chances are you will not pass this class.I encourage you to educate yourself in online learning so that you can make sure this class truly suits your needs. I do not want you to waste many and time.  The following describes some general information about online learning so that you can make educated choices.\noindent\begin{bf}What is a fully Online class and a hybrid class?\end{bf}\parA fully online course are Web-delivered courses. These are classes taught through the Internet at the distance. This means you will take the class with your laptop, tablet or even your smartphone. Online courses are also distant in time and normally you do not have to be online at a specific time taking the course. Hybrid online classes have a face-to-face component. This means you are required to attend a physical class normally once a weak. Online classes are not face-to-face classes and hence you will not have as instructor guiding your learning. You will have to be more independent, proactive and organized in order to submit your assignments on time and study for the different terms.\noindent\begin{bf} Online learning and comfort\end{bf}\parOne of the benefits of online education is the fact that there are no physical class sessions. This is not true for hybrid classes that contain a face to face component that need to be fulfilled. As an online student you will have to read lecture material and complete assignments sending them electronically, with no need to fight traffic, leave work early for class, or miss important family time. Online courses give you the opportunity to plan study time around the rest of their day. You can study and work at your convenience. \noindent\begin{bf} Time management\end{bf}\parOnline courses require a lot of time and intensive work. Unless you are very organized and have a strict discipline chances are you will not pass this class. During online study time management is a difficult task. You might not have enough time during your day to study due to their various everyday commitments and that will certainly affect your chances to succeed in an online class. A regular schedule planner would be a significant help and you can even set reminders for your courses and assignments.\noindent\begin{bf} Self-Motivation\end{bf}\parSelf-motivation is an eLearning essential requirement; if you lack this quality you will certainly struggle while studying online and even fail.You need to find the motivation to follow an online calendar with numerous study hours and assignments and no-one but you to push you through the semester. Only a positive attitude will help you overcome the challenges in eLearning.\noindent\begin{bf} Computer Literacy\end{bf}\parTechnological proficiency is a must for online courses, as it enables you to manage assignments and courseware in an organized manner without struggling. You might think you are tech savvy, and thus able to manage computers well. However, lack of computer literacy is a major issue among online students. You might not be able to operate basic programs such as Microsoft Word and PowerPoint and therefore are not able to handle their files. More importantly, you have to be an expert in blackboard. 

\end{multicols*}
\end{fullwidth}
\restoregeometry
\end{document}
